---
title: "GoT Hendrik Vanb – Beyound map"
author: "Eirik Lamøy"
date: "16 3 2020"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

A go thourgh of these exlent [slides](https://hendrikvanb.gitlab.io/slides/purrr_beyond_map.html#28).


## write and read files with pwalk


### Write
```{r}

library(tidyverse)

# Check for file, the command shows that dere are no files at the dir.
list.files("data/mpg")

# create files by taking the mpg df %>% collapsing the data for each manufacturer into a list column %>% walking over the two columns in the df and for each pair (i.e. row of manufacturer and data values) doing: {create path variable to point to the path where the data should be written %>% write the data to disk in .csv format}

mpg %>% 
  group_nest(manufacturer, keep = T) %>% 
  pwalk( function(manufacturer, data) {
    # Create each path for each file 
    path <- file.path("data/mpg", glue::glue("df_{manufacturer}.csv") )  
    # Write each file  
    write_csv(data, path)
  })



```

Effectiv check and print files from a directory

```{r}

list.files("data/mpg") %>%  {c(head(., 2), tail(.,2) )}



```

### Read

Read each of the .csv files just written to disk into R's global environment as a data frames. Use each file's name (without the .csv extension) as the name for its data frame.

```{r}
# Check that there is no files:
ls()

list.files("data/mpg", pattern = ".csv", full.names = T) %>%  
  set_names(str_remove(basename(.), pattern = ".csv$" )) %>% 
  iwalk( function(x,i) assign(i,data.table::fread(x), .GlobalEnv))

# Files should now be in th global envirment
ls() %>% {c(head(.,2) , tail(., 2))}


```

## modify_* 

Example: For each manufacturer in the mpg dataset, express all of the numeric columns as the % deviation from the mean

1) Define a function

```{r}
my_fun <- function(x) {(x/mean(x,na.rm = T))-1}

```

dplyr approach
```{r}
# dplyr-way
mpg %>% 
  group_by(manufacturer) %>% 
  mutate_if( is.numeric, function(x) {x^2}) %>% 
  ungroup()


```


The data.table -way

```{r}
library(data.table)
mpg %>% 
  setDT( ) %>% 
  .[by = .(manufacturer), j = modify_if(.SD, is.numeric, function(x) x^2)]
```


## Predicate functionals
Predicate functional is a function that return TRUE or FALSE,
Arg. vector X, and predicate .f ->


Example:
For which manufacturers in the mpg dataset do the city miles per gallon (cty) (a) exceed 15mpg on all models and/or (b) 25 mpg on at least some models?


```{r}

map_lgl( c(1:5), function(x) { x > 3})
some(c(1:5), function(x) { x > 3})
every(c(1:5), function(x) { x > 3})

mpg %>%
  group_by(manufacturer) %>% 
  summarise( cyl_all_above_15 = every(cty, function(x) x >15),
             cyl_some_above_25 = some(cty, function(x) x > 25)) %>% 
  ungroup()


```

### every/some used with filter

```{r}
# take mpg %>% group by manufacturer %>% filter to
# keep only data for manufacturers whose models all
# have cty > 15mpg

mpg %>% group_by(manufacturer) %>% 
  filter( every( cty, function(x) {x > 15}))

```


## reduce() and accumulate()
- Collasing and building it up:



## Adverbs: 

Compose and partial

Compose

```{r}
round( mean( seq(from = 0.1, to = 5, length.out = 12), na.rm = T), digits = 1)

round( mean( seq(from = 0.2, to = 10, length.out = 12), na.rm = T), digits = 1)

# Simplify

my_round_sum <- compose(~ mean(.x, na.rm = T),
                        ~ round(.x, digits = 1),
                        .dir = "forward")


fun1 <- as_mapper( ~mean(.x, na.rm = T))
fun2 <- as_mapper( function(x) {mean(x, na.rm = T)})
fun3 <- as_mapper( function(x) {round(x, digits = 1)})

my_round_sum(seq(from = 0.1, to = 5, length.out = 12))

```


partial

```{r}
round(0.921241, digits = 2)

my_round <- partial(round, digits = 2)

my_round(0.012)



```

## Reduce and accumulate

reduce(.x, .f, ..., .init)
use function .f to combine elements of .x by passing
the result of each itteration as an initial value to the next
itteration; return single result from nal itteration

accumulate(.x, .f, ..., .init)
use function .f to combine elements of .x by passing
the result of each itteration as an initial value to the next
itteration; return list of results from each itteration


```{r}
reduce(lettes[seq(1:5)], str_c )
```



### Compose for efficient model-calculation


```{r}
mpg %>% head()

models <- c("trans", "drv", "class") %>%  accumulate( function(x,y)  { paste(x,y, sep = " + ") }, .init = "cty ~ manufacturer"  ) %>%  set_names(1:length(.)) 

enframe(models, name = "model", value = "spec") 


```


```{r}
# take models %>% estimate each using map to apply
# the lm function %>% get the summary for each set of
# results using map to apply the summary function %>%
# extract the adjusted r-squared for each set of
# summary results using map_dbl to extract it by name
# %>% print the results in a neatly formatted tibble

models %>% 
  map(lm , data = mpg) %>% 
  map(summary) %>% 
  map_dbl( "adj.r.squared") %>% 
  enframe(name = "model", value = "Adj-R2") %>% janitor::clean_names()
```


### With compose:

```{r}
my_comp <- compose(lm, summary, 
                   ~pluck(.x, "adj.r.squared"),
                   ~enframe(.x, name = "model", value = "adj.r.squared"),
                   .dir = "forward")

models %>% map_dfr(~my_comp(.x, data = mpg))

```


## Self-test

```{r}

models <- c("trans", "drv", "class") %>%  accumulate( function(x,y)  { paste(x,y, sep = " + ") }, .init = "cty ~ manufacturer"  ) %>%  set_names(1:length(.)) 



c("trans", "drv", "class")

c("trans", "drv", "class") %>%
  accumulate(function(x, y) { str_c(x, y , sep = "+") }, .init = "city ~ manufacturer")

# As a list
models <-  list(a = "Eirik", b=  "Trond") %>%
  accumulate(function(x, y) { str_c(x, y , sep = "+") }, .init = "city ~ manufacturer")

enframe(models, name = "model", value = "spec") 



```










